Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Add Leah's contributions to discussion

# Discussion
In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using nonlinear dynamical time series analyses, we investigated the 
theory that virtual mobilization is increasingly reflective of real-world 
events during times of strife.

@@

(This would be where Leah should update her part.)

## Conclusion
Given the pervasiveness of social media, it is unsurprising
that social activists and protesters have
utilized these platforms to support real-world mobilization. 
Here, we quantitatively explored the connection
between online social cohesion and real-world events. In addition
to introducing political scientists to a family of powerful nonlinear 
dynamics analyses, our results have serious implications for monitoring global
movements. While traditional media in regions of authoritarian rule are
often biased, the self-organized nature of Twitter poses a new avenue to gain
insight into truths about uprisings and social mobilization. By
conceptualizing Twitter and real-world events as two elements of an
inextricably linked dynamical system, the levels of social cohesion within 
social media platforms could be monitored for fluctuations indicating shifts
in power and peace. Social media mobilization may thus help alert the world to
citizens' actions and reactions that are suppressed by government regimes,
providing insight into events that may not otherwise be broadcast.

>>>>

# Discussion
In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring. 
CRQA methodology allows us to model the relationship between sociolinguistic 
cohesion and exogenous political events. This work stands alongside the model 
of Palestinian-Israeli social media and events developed by Zeitzoff (2011), 
and the role of peripheral participants in the Syrian Arab Spring movement by 
Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we 
demonstrate how language and social mobilization interact with events along 
the conflict-cooperation continuum in Syria. We have introduced a novel 
theoretical framework of sociolinguistic cohesion which we operationalize 
using a weighted measure of lexical relationships. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using nonlinear dynamical time series analyses, we investigated the 
theory that virtual mobilization is increasingly reflective of real-world 
events during times of strife.

@@

This methodology should be of great interest to social scientists investigating social mobilization. It has potential applications for gender studies and the #MeToo movement, and for the relationship between social protest and repression during the Black Lives Matter protests. Fundamentally, this methodological approach can help us better understand the mechanisms underlying social media, and its influence on human behavior in real life. Given that many governments enact repressive measures when they determine that collective action by citizens has become an imminent possibility this methodology should help to improve the predictive power of using social media data in estimating repressive behavior. If social media messages are increasing in cohesion, this may represent a threat to civil and political liberties of citizens engaging in collective action.

## Conclusion
Considering the pervasiveness of social media, it is unsurprising
that social activists and protesters have
utilized these platforms to support real-world mobilization. 
Here, we quantitatively explored the connection
between online social cohesion and real-world events. In addition
to introducing political scientists to a family of powerful nonlinear 
dynamics analyses, our results have serious implications for monitoring global
movements in consistent across other social uprisings. While traditional, 
state-run media in regions of authoritarian rule are often biased and 
propaganda for the leader and central government, the 
self-organized nature of Twitter poses a new avenue to gain insight into 
truths about up-risings and social mobilization. By conceptualizing Twitter 
and real-world events as two elements of an inextricably linked dynamical 
system, the levels of social cohesion within social media platforms could be 
monitored for fluctuations indicating shifts in power and peace. Social media
mobilization may thus help alert the world to citizens' actions and reactions 
that are suppressed by government regimes, providing insight into events that 
may not otherwise be broadcast and allowing for faster intervention.

### 2020-06-01 manuscript.tex
Add Leah's contributions to discussion

In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using nonlinear dynamical time series analyses, we investigated the
theory that virtual mobilization is increasingly reflective of real-world
events during times of strife.

@@

(This would be where Leah should update her part.)

@@

Given the pervasiveness of social media, it is unsurprising
that social activists and protesters have
utilized these platforms to support real-world mobilization.
Here, we quantitatively explored the connection
between online social cohesion and real-world events. In addition
to introducing political scientists to a family of powerful nonlinear
dynamics analyses, our results have serious implications for monitoring global
movements. While traditional media in regions of authoritarian rule are
often biased, the self-organized nature of Twitter poses a new avenue to gain
insight into truths about uprisings and social mobilization. By
conceptualizing Twitter and real-world events as two elements of an
inextricably linked dynamical system, the levels of social cohesion within
social media platforms could be monitored for fluctuations indicating shifts
in power and peace. Social media mobilization may thus help alert the world to
citizens' actions and reactions that are suppressed by government regimes,
providing insight into events that may not otherwise be broadcast.

>>>>

In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring.
CRQA methodology allows us to model the relationship between sociolinguistic
cohesion and exogenous political events. This work stands alongside the model
of Palestinian-Israeli social media and events developed by Zeitzoff (2011),
and the role of peripheral participants in the Syrian Arab Spring movement by
Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
demonstrate how language and social mobilization interact with events along
the conflict-cooperation continuum in Syria. We have introduced a novel
theoretical framework of sociolinguistic cohesion which we operationalize
using a weighted measure of lexical relationships. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using nonlinear dynamical time series analyses, we investigated the
theory that virtual mobilization is increasingly reflective of real-world
events during times of strife.

@@

This methodology should be of great interest to social scientists investigating social mobilization. It has potential applications for gender studies and the \#MeToo movement, and for the relationship between social protest and repression during the Black Lives Matter protests. Fundamentally, this methodological approach can help us better understand the mechanisms underlying social media, and its influence on human behavior in real life. Given that many governments enact repressive measures when they determine that collective action by citizens has become an imminent possibility this methodology should help to improve the predictive power of using social media data in estimating repressive behavior. If social media messages are increasing in cohesion, this may represent a threat to civil and political liberties of citizens engaging in collective action.

@@

Considering the pervasiveness of social media, it is unsurprising
that social activists and protesters have
utilized these platforms to support real-world mobilization.
Here, we quantitatively explored the connection
between online social cohesion and real-world events. In addition
to introducing political scientists to a family of powerful nonlinear
dynamics analyses, our results have serious implications for monitoring global
movements in consistent across other social uprisings. While traditional,
state-run media in regions of authoritarian rule are often biased and
propaganda for the leader and central government, the
self-organized nature of Twitter poses a new avenue to gain insight into
truths about up-risings and social mobilization. By conceptualizing Twitter
and real-world events as two elements of an inextricably linked dynamical
system, the levels of social cohesion within social media platforms could be
monitored for fluctuations indicating shifts in power and peace. Social media
mobilization may thus help alert the world to citizens' actions and reactions
that are suppressed by government regimes, providing insight into events that
may not otherwise be broadcast and allowing for faster intervention.
